---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures",
  out.width = "100%"
)
library(hausekeep) # load package
```
# hausekeep

[![Travis build status](https://travis-ci.org/hauselin/hausekeep.svg?branch=master)](https://travis-ci.org/hauselin/hausekeep) [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hauselin/hausekeep?branch=master&svg=true)](https://ci.appveyor.com/project/hauselin/hausekeep) [![Coverage status](https://codecov.io/gh/hauselin/hausekeep/branch/master/graph/badge.svg)](https://codecov.io/github/hauselin/hausekeep?branch=master) 

[![DOI](https://zenodo.org/badge/168783741.svg)](https://doi.org/10.5281/zenodo.2555874)

Functions to make it easier to analyse and summarise data and results in R. For documentation, see https://hauselin.github.io/hausekeep/ Also check out my R tutorials [here](https://hausetutorials.netlify.com/).

## Installation

To install the package, type the following commands into the R console:

```r
# install.packages("devtools")
devtools::install_github("hauselin/hausekeep") # you might have to install devtools first (see above)
```

## Examples

### `summaryh()` generates formatted results and effect sizes for manuscripts

Generate model summaries that can be copied and pasted straight into your manuscript (no more copy-paste frustrations and errors!). Summaries are formatted according to American Psychological Association (APA) guidelines (get in touch if you require other formats). Example APA summaries generated by `summaryh()`: 

* regression output: b = 1.41, SE = 0.56, t(30) = 2.53, p = .017, r = 0.42
* ANOVA output: F(1, 30) = 9.00, p = .005, r = 0.48
* t-test output:  t(23) = −4.67, p < .001, r = 0.70

```r
model_lm <- lm(mpg ~ cyl, mtcars) 
summary(model_lm) # base R summary()
summaryh(model_lm) # returns APA-formatted output in a data.table
summaryh(model_lm, decimal = 5, showTable = T, showEffectSizesTable = T) # optional arguments

# linear mixed effects regression
library(lme4); library(lmerTest) # load packages to fit mixed effects models
model <- lmer(weight ~ Time * Diet  + (1 + Time | Chick), data = ChickWeight)
summary(model) # standard summary
summaryh(model)
summaryh(model, decimal = 4, showTable = T, showEffectSizesTable = T) # optional arguments

# ANOVA
summaryh(aov(mpg ~ gear, mtcars))

# correlation
cor.test(mtcars$mpg, mtcars$cyl)
summaryh(cor.test(mtcars$mpg, mtcars$cyl))
summaryh(cor.test(mtcars$mpg, mtcars$cyl), 3, T, T)
```

### `es()` converts between effect size measures

The `es` function converts one effect size into other effect sizes (e.g., d, r, R<sup>2</sup>, f, odds ratio, log odds ratio, area-under-curve [AUC]). Also available as a [Shiny app](http://escal.site).

```{r es example}
es(d = 0.2)

es(r = c(0.1, 0.4, 0.7))
```

### `outliersMAD()` identifies outliers using robust median absolute deviation approach

```{r}
example <- c(1, 3, 3, 6, 8, 10, 10, 1000) # 1000 is an outlier
outliersMAD(example) # MAD approach
```

### `outliersZ()` identifies outliers using Z-score cut-off

```{r}
example <- c(1, 3, 3, 6, 8, 10, 10, 1000) # 1000 is an outlier
outliersZ(example) # SD approach

# compare with MAD approach from above
outliersZ(example) # SD approach
```

### `fit_ezddm()` fits EZ-diffusion model for two-choice response time tasks

```r
library(rtdists) # load package to help us simulate some data
data1 <- rdiffusion(n = 100, a = 2, v = 0.3, t0 = 0.5, z = 0.5 * 2) # simulate data
data2 <- rdiffusion(n = 100, a = 2, v = -0.3, t0 = 0.5, z = 0.5 * 2) # simulate data
dataAll <- rbind(data1, data2) # join data
dataAll$response <- ifelse(dataAll$response == "upper", 1, 0) # convert responses to 1 and 0
dataAll$subject <- rep(c(1, 2), each = 100) # assign subject id
dataAll$cond1 <- sample(c("a", "b"), 200, replace = T) # randomly assign conditions a/b
dataAll$cond2 <- sample(c("y", "z"), 200, replace = T) # randomly assign conditions y/z

# fit model to just entire data set (assumes all data came from 1 subject)
fit_ezddm(data = dataAll, rts = "rt", responses = "response")
# fit model to each subject (no conditions)
fit_ezddm(data = dataAll, rts = "rt", responses = "response", id = "subject") 
# fit model to each subject by cond1
fit_ezddm(data = dataAll, rts = "rt", responses = "response", id = "subject", group = "cond1") 
# fit model to each subject by cond1,cond2
fit_ezddm(data = dataAll, rts = "rt", responses = "response", id = "subject", group = c("cond1", "cond2"))
```

### `sca_lm()` fits every possible linear regression model given a set of predictors and covariates

`sca_lm()` is a basic implementation of [specification curve analysis](http://sticerd.lse.ac.uk/seminarpapers/psyc16022016.pdf) for linear regression.

```r
# models to fit: mpg ~ cyl; mpg ~ carb; mpg ~ cyl + carb
sca_lm(data = mtcars, dv = "mpg", ivs = c("cyl", "carb")) # default no covariates 

# models to fit (with and without covariate vs): mpg ~ cyl; mpg ~ carb; mpg ~ cyl + carb
sca_lm(data = mtcars, dv = "mpg", ivs = c("cyl", "carb"), covariates = "vs")
```
